---
title: "CE2_Martinoli_Travaglini"
author: "Francesca Martinoli, Simone Travaglini"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1: inspect the *robots.txt*

Inspecting the **robots.txt** page for the blog [beppegrillo.it](https://beppegrillo.it/), we can see that it returns a 404 error (which means that the page it's "not found"), because **beppegrillo.it** does not have a robots.txt page. In such situation we can proceed with the scraping using a politely method, which includes:

-   Be identifiable with ***User-Agent*** and ***From*** header fields

-   Scrape as few as possible

-   Do not bombard the server

## Task 2: download the page in a politely way

```{r, eval = F}
library(RCurl)
url <- "https://beppegrillo.it/un-mare-di-plastica-ci-sommergera/"
resp <- RCurl::getURL(url = url, httpheader = c(from = "my@email.com", 'User-Agent' = R.Version()$version.string))

```

There are many ways to get and download pages from the web using R. We used the function [*getURL*]{.underline} from the package [**RCurl**]{.underline}. First of all, we create an object called ***url*** which contains the link to the page ["un mare di plastica ci sommergerà"](https://beppegrillo.it/un-mare-di-plastica-ci-sommergera/) from **beppegrillo.it**. Then we used this object into the function ***getURL***, in which we added an header which contains our email and our 'User-Agent' in order to making a politely request. We stored the response at this request into an object called ***resp***.

## Task 3: get all the HTML links and keep only those which re-direct to other post of blog

First, we got all the links from the page (stored into ***resp***) using the function [*getHTMLLinks*]{.underline} from the package [**XML**]{.underline}. 

```{r, eval = F}
library(XML)
links <- XML::getHTMLLinks(resp, externalOnly = T)
```
We stored the links into an object called ***links***, then we transformed it into a data frame (called ***data***), using the function [**tibble**]{.underline}. 

```{r, eval = F}
data <- tibble(links)
```
Then, we need to keep only those links that re-direct to other posts of the **beppegrillo.it** blog. In order to do this, we used a regular expression into the function **stringr::str_extract_all** that match only the links we need: this regex allows us to match only the links of other post and not e.g. the links for the sections of the blog. 

```{r, eval = F}
library(stringr)
link_grillo <- str_extract_all(
  links_unl, pattern = "^https://beppegrillo\\.it/[^category].+")

link_grillo <- unlist(link_grillo)
link_grillo2 <- as.data.frame(link_grillo)

```
The regular expression used for extract the links is **^https://beppegrillo\\.it/[^category].+**.

We stored the result into an object called ***link_grillo*** and then we transofmed it into a data frame using the function [*as.data.frame*]{.underline}.


## Task 4: scrape all the posts for 2016

First of all we create a new function [*download_politely*]{.underline} that allows us to get and download pages in a politely way.

```{r, eval = F}
download_politely <- function(from_url, to_html, my_email, my_agent = R.Version()$version.string) {
  
  require(httr)
  
  # Check that arguments are inputted as expected:
  stopifnot(is.character(from_url))
  stopifnot(is.character(to_html))
  stopifnot(is.character(my_email))
  
  # GET politely
  grillo_16 <- httr::GET(url = from_url, 
                         add_headers(
                           From = my_email, 
                           `User-Agent` = R.Version()$version.string
                         )
  )
  # If status == 200, extract content and save to a file:
  if (httr::http_status(grillo_16)$message == "Success: (200) OK") {
    bin <- content(grillo_16, as = "raw")
    writeBin(object = bin, con = to_html)
  } else {
    cat("Houston, we have a problem!")
  }
}
```
Then we crated a vector with the links of the 47 pages of the archive for 2016, and we used it into a for loop to download all the links into a folder called ***grillo_linkpages***, using the function [*download_politely]{.underline}.

```{r, eval = F}
link <- str_c("https://beppegrillo.it/category/archivio/2016/page/", 1:47)

dir.create("grillo_linkpages")

for (i in seq_along(link)) {
  cat(i, " ")
  
  download_politely(from_url = link[i], 
                    to_html = here::here("grillo_linkpages", str_c("page_",i,".html")), 
                    my_email = "francescamartinoli@yahoo.com")
  
  Sys.sleep(0.5)
}

```
In order to get and download the 47 pages we set **Sys.sleep(0.5)**. 



## Task 5
